\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-08-25 sections/abstract.tex
Change: Update abstract and results

\section*{Importance}
  To understand and control the mechanisms that determine the structure and function of microbial communities, it is important to map the interrelationships between its constituent microbial species.
  The surge in the high-throughput sequencing of microbial communities has led to the creation of thousands of datasets containing information about microbial abundances.
  These abundances can be transformed into networks of co-occurrences across multiple samples, providing a glimpse into the structure of microbiomes.
  However, processing these datasets to obtain co-occurrence information relies on several complex steps, each of which involves numerous choices of tools and corresponding parameters.
  These multiple options pose questions about the accuracy and uniqueness of the inferred networks.
  In this study, we address this workflow and provide a systematic analysis of how these choices of tools and parameters affect the final network, and on how to select those that are most appropriate for a particular dataset.
  We also develop a consensus network algorithm that helps generate more robust and accurate occurrence networks based on benchmarks synthetic datasets.

>>>>

\section*{Importance}
  Mapping the interrelationships between the species in a microbial community is essential to understand and control their structure and function.
  The surge in the high-throughput sequencing of microbial communities has led to the creation of thousands of datasets containing information about microbial abundances.
  These abundances can be transformed into co-occurrence networks, providing a glimpse into the associations within microbiomes.
  However, processing these datasets to obtain co-occurrence information relies on several complex steps, each of which involves numerous choices of tools and corresponding parameters.
  These multiple options pose questions about the accuracy and uniqueness of the inferred networks.
  In this study, we address this workflow and provide a systematic analysis of how these choices of tools affect the final network, and guidelines on appropriate tool selection for a particular dataset.
  We also develop a consensus network algorithm that helps generate more robust and accurate occurrence networks based on benchmarks synthetic datasets.

### 2022-08-25 sections/coverpage.tex
Change: Update abstract and results

  \vspace{1.5 cm}
  Dileep Kishore\textsuperscript{1},
  Gabriel Birzu\textsuperscript{2},
  Zhenjun Hu\textsuperscript{1},
  Charles DeLisi\textsuperscript{1,3},
  Kirill Korolev\textsuperscript{$\dagger$1,2},\\
  Daniel Segr\`{e}\textsuperscript{$\dagger$1,3,4}\\
  \vspace{1cm}
  \textsuperscript{1}Bioinformatics Program, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{2}Department of Physics, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{3}Department of Biomedical Engineering, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{4}Department of Biology, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{$\dagger$}Correspondence should be sent to \href{mailto:korolev@bu.edu}{korolev@bu.edu} or \href{mailto:dsegre@bu.edu}{dsegre@bu.edu}\\

>>>>

  \vspace{1.5 cm}
  Dileep Kishore\textsuperscript{a,b},
  Gabriel Birzu\textsuperscript{c,f},
  Zhenjun Hu\textsuperscript{a},
  Charles DeLisi\textsuperscript{a,c},
  Kirill S. Korolev\textsuperscript{a,b,c}\#,\\
  Daniel Segr\`{e}\textsuperscript{a,b,d,e}\#\\
  \vspace{1cm}
  \textsuperscript{a}Bioinformatics Program, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{b}Biological Design Center, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{c}Department of Physics, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{d}Department of Biomedical Engineering, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{e}Department of Biology, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{f}Department of Applied Physics, Stanford University, Stanford, California, USA\\
  \textsuperscript{$\#$}Correspondence should be sent to \href{mailto:korolev@bu.edu}{korolev@bu.edu} or \href{mailto:dsegre@bu.edu}{dsegre@bu.edu}\\

  \vspace{2cm}
  % TODO: Add word count
  Abstract word count: 244\\
  Text word count: \\
